### 2022-06-21 publications.tex
Newcool paper submitted

\begin{benumerate}{16}
\item \textit{Slow Star Formation in the Milky Way: Theory Meets Observations}\\
  Evans, Neal J., II, \textbf{Kim, J.-G.}, \& Ostriker, E. C. 2022, ApJL, 929L,
  18E
\item \textit{Star Formation Regulation and Self-Pollution by Stellar Wind
    Feedback}\\
  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G. 2021, ApJL,
  922L, 3L
\item \textit{Efficiently Cooled Stellar Wind Bubbles in Turbulent Clouds:
    II. Validation of Theory with Hydrodynamic Simulations}\\
  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G. 2021, ApJ,
  914, 90L
\item \textit{Efficiently Cooled Stellar Wind Bubbles in Turbulent Clouds:
I. Fractal Theory and Application to Star-Forming Clouds}\\
  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G., 2021, ApJ,
914, 89L
\item \textit{Star Formation Efficiency and Dispersal of Giant Molecular
    Clouds with UV Radiation Feedback: Dependence on Gravitational Boundedness
    and Magnetic Fields} \\ \textbf{Kim, J.-G.}, Ostriker, E. C., \& Filippova,
  N. 2021, ApJ, 911, 128K
\item \textit{The environmental dependence of the $X_{\mathrm CO}$ conversion
    factor}\\ Gong, M., Ostriker, E. C., Kim, C.-G., \& \textbf{Kim,
    J.-G.} 2020, ApJ, 903, 142 
\item \textit{Factories of CO-dark gas: molecular clouds with limited star
formation efficiencies by far-ultraviolet feedback} \\
  Inoguchi, M., Hosokawa, T., Mineshige, S., \& \textbf{Kim, J.-G.} 2020, MNRAS,
  497, 5061I
\item \textit{\# Diffuse Ionized Gas in Simulations of Multiphase, Star-forming
    Galactic Disks}\\
  Kado-Fong, E., \textbf{Kim, J.-G.}, Ostriker, E. C., \& Kim, C.-G. 2020, ApJ,
  897, 143
\item \textit{Modeling UV Radiative Feedback from Massive Stars: III. Escape
    of Radiation from Star-Forming Giant Molecular Clouds} \\ \textbf{Kim,
    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, ApJ, 883, 102
\item \textit{Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
of Star-Forming Giant Molecular Clouds by Photoionization and Radiation
Pressure} \\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, ApJ, 859,
68
\item \textit{Modeling UV Radiative Feedback from Massive Stars: I.
Implementation of Adaptive Ray Tracing Method and Tests}\\ \textbf{Kim, J.-G.},
Kim, W.-T., Ostriker, E. C.,\& Skinner A. M. 2017, ApJ, 851, 93
\item \textit{Disruption of Molecular Clouds by Expansion of Dusty H II
Regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
137
\item \textit{Instability of Magnetized Ionization Fronts Surrounding H II
regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
\item \textit{Nature of Wiggle Instability of Galactic Spiral Shocks}\\ Kim,
W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
\item \textit{Instability of Evaporation Fronts in the Interstellar Medium}\\
  \textbf{Kim, J.-G.}, Kim, W.-T. 2013, ApJ, 779, 48
\item \textit{Gravitational Instability of Rotating, Pressure-Confined,
    Polytropic Gas Disks with Vertical Stratification} \\ \textbf{Kim, J.-G.},
  Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012, ApJ, 761, 131
\end{benumerate}

\subsection{Papers in Preparation}
\begin{enumerate}
\item[] \textit{Photochemistry and Heating/Cooling of the Multiphase
    Interstellar Medium with UV Radiative Transfer} \\ \textbf{Kim, J.-G.},
  Gong, M., Kim, C.-G., \& Ostriker, E. C. \textit{2022, to be submitted}
\item[] \textit{What Regulates Galactic Star Formation Rates? A View from New
    TIGRESS Simulations} \\ Kim, C.-G., \textbf{Kim, J.-G.}, Gong, M., Ostriker,
  E. C. \textit{2022, to be submitted}
\item[] \textit{Destruction of Giant Molecular Clouds by Stellar Feedback: I.
    Relative Importance of Radiation, Winds, and Supernovae} \\ \textbf{Kim,
    J.-G.}, Lancaster, L., Kim, C.-G., \& Ostriker, E. C. \textit{2022, in
    prep.}
\item[] \textit{The Lyman Continuum and Far-UV Interstellar Radiation Field in
    Simulations of Multiphase, Star-forming Galactic Disks} \\ Linzer, N.,
  \textbf{Kim, J-.G.}, Ostriker, E. C., Kim, C.-G. \textit{2022, in prep.}
\item[] \textit{Bubble Expansion Driven by Stellar Winds and Radiation in
    Turbulent, Magnetized Clouds} \\ Lancaster, L., Ostriker, E. C.,
  \textbf{Kim, J.-G.}, Kim, C.-G. \textit{2022, in prep.}
\item[] \textit{Modeling Polarized Thermal Emission from Dust Grains in Low-Mass
    Protostellar Cores with POLARIS} \\ Giang, N. C., Hoang, T., \& \textbf{Kim,
    J.-G.} \textit{2022, in prep.}
% \item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case
%     of M15} \\
%   Hotokezaka, K., \textbf{Kim, J.-G.}, Beniamini, P., \& Cen, R. \textit{in prep.}
 % \item[] \textit{Recovery of Cloud-Scale Star Formation Rate Based on Ionizing
 %    Luminosity: Calibration for Escape of Radiation} \\ \textbf{Kim, J.-G.} \&
 %  Ostriker, E. C. \textit{in prep.}
\end{enumerate}

>>>>

\begin{benumerate}{17}
\item \textit{Photochemistry and Heating/Cooling of the Multiphase
    Interstellar Medium with UV Radiative Transfer} \\ \textbf{Kim, J.-G.},
  Gong, M., Kim, C.-G., \& Ostriker, E. C. \textit{ApJ submitted}
\item \textit{Slow Star Formation in the Milky Way: Theory Meets Observations}\\
  Evans, Neal J., II, \textbf{Kim, J.-G.}, \& Ostriker, E. C. 2022, ApJL, 929L,
  18E
\item \textit{Star Formation Regulation and Self-Pollution by Stellar Wind
    Feedback}\\
  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G. 2021, ApJL,
  922L, 3L
\item \textit{Efficiently Cooled Stellar Wind Bubbles in Turbulent Clouds:
    II. Validation of Theory with Hydrodynamic Simulations}\\
  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G. 2021, ApJ,
  914, 90L
\item \textit{Efficiently Cooled Stellar Wind Bubbles in Turbulent Clouds:
I. Fractal Theory and Application to Star-Forming Clouds}\\
  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G., 2021, ApJ,
914, 89L
\item \textit{Star Formation Efficiency and Dispersal of Giant Molecular
    Clouds with UV Radiation Feedback: Dependence on Gravitational Boundedness
    and Magnetic Fields} \\ \textbf{Kim, J.-G.}, Ostriker, E. C., \& Filippova,
  N. 2021, ApJ, 911, 128K
\item \textit{The environmental dependence of the $X_{\mathrm CO}$ conversion
    factor}\\ Gong, M., Ostriker, E. C., Kim, C.-G., \& \textbf{Kim,
    J.-G.} 2020, ApJ, 903, 142 
\item \textit{Factories of CO-dark gas: molecular clouds with limited star
formation efficiencies by far-ultraviolet feedback} \\
  Inoguchi, M., Hosokawa, T., Mineshige, S., \& \textbf{Kim, J.-G.} 2020, MNRAS,
  497, 5061I
\item \textit{\# Diffuse Ionized Gas in Simulations of Multiphase, Star-forming
    Galactic Disks}\\
  Kado-Fong, E., \textbf{Kim, J.-G.}, Ostriker, E. C., \& Kim, C.-G. 2020, ApJ,
  897, 143
\item \textit{Modeling UV Radiative Feedback from Massive Stars: III. Escape
    of Radiation from Star-Forming Giant Molecular Clouds} \\ \textbf{Kim,
    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, ApJ, 883, 102
\item \textit{Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
of Star-Forming Giant Molecular Clouds by Photoionization and Radiation
Pressure} \\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, ApJ, 859,
68
\item \textit{Modeling UV Radiative Feedback from Massive Stars: I.
Implementation of Adaptive Ray Tracing Method and Tests}\\ \textbf{Kim, J.-G.},
Kim, W.-T., Ostriker, E. C.,\& Skinner A. M. 2017, ApJ, 851, 93
\item \textit{Disruption of Molecular Clouds by Expansion of Dusty H II
Regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
137
\item \textit{Instability of Magnetized Ionization Fronts Surrounding H II
regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
\item \textit{Nature of Wiggle Instability of Galactic Spiral Shocks}\\ Kim,
W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
\item \textit{Instability of Evaporation Fronts in the Interstellar Medium}\\
  \textbf{Kim, J.-G.}, Kim, W.-T. 2013, ApJ, 779, 48
\item \textit{Gravitational Instability of Rotating, Pressure-Confined,
    Polytropic Gas Disks with Vertical Stratification} \\ \textbf{Kim, J.-G.},
  Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012, ApJ, 761, 131
\end{benumerate}

\subsection{Papers in Preparation}
\begin{enumerate}
\item[] \textit{What Regulates Galactic Star Formation Rates? A View from New
    TIGRESS Simulations} \\ Kim, C.-G., \textbf{Kim, J.-G.}, Gong, M., Ostriker,
  E. C. \textit{2022, to be submitted}
\item[] \textit{Destruction of Giant Molecular Clouds by Stellar Feedback: I.
    Relative Importance of Radiation, Winds, and Supernovae} \\ \textbf{Kim,
    J.-G.}, Lancaster, L., Kim, C.-G., \& Ostriker, E. C. \textit{2022, in
    prep.}
\item[] \textit{The Lyman Continuum and Far-UV Interstellar Radiation Field in
    Simulations of Multiphase, Star-forming Galactic Disks} \\ Linzer, N.,
  \textbf{Kim, J-.G.}, Ostriker, E. C., Kim, C.-G. \textit{2022, in prep.}
\item[] \textit{Bubble Expansion Driven by Stellar Winds and Radiation in
    Turbulent, Magnetized Clouds} \\ Lancaster, L., Ostriker, E. C.,
  \textbf{Kim, J.-G.}, Kim, C.-G. \textit{2022, in prep.}
\item[] \textit{Modeling Polarized Thermal Emission from Dust Grains in Low-Mass
    Protostellar Cores with POLARIS} \\ Giang, N. C., Hoang, T., \& \textbf{Kim,
    J.-G.} \textit{2022, in prep.}
% \item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case
%     of M15} \\
%   Hotokezaka, K., \textbf{Kim, J.-G.}, Beniamini, P., \& Cen, R. \textit{in prep.}
 % \item[] \textit{Recovery of Cloud-Scale Star Formation Rate Based on Ionizing
 %    Luminosity: Calibration for Escape of Radiation} \\ \textbf{Kim, J.-G.} \&
 %  Ostriker, E. C. \textit{in prep.}
\end{enumerate}
